---
title: "Shiny Happy Hour"
subtitle: "BioData Club/PDX-R"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include = FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "midnightblue",
  header_font_google = google_font("Josefin Sans"),
  link_color = "steelblue",
  text_font_size = "24px",
  footnote_font_size = "20px",code_inline_font_size = "19px"
)
```

class: center, middle

# Welcome to the Shiny Happy Hour

---
# This is a Joint Event

- BioData Club (OHSU)
- PDX-R User Group

---
# What is BioData Club?

- https://biodata-club.github.io/

> BioData Club is an interdisciplinary community at OHSU dedicated to promoting a fun and supportive culture of co-learning in data science skills and open science principles. We host workshops and social events where attendees can learn and work on projects among friends and colleagues. Biodata Club welcomes everyone who wants to better their know-how in all things data, regardless of skill level. We want to replace statistics anxiety and code fear with inspiration and motivation to learn and share. BioData Club is supported by the OHSU Library and DMICE.

---
# What is PDX R User Group?

- https://pdxrlang.com

> We are the R user group for Portland, Oregon. Our goal is to support and share R experience and knowledge among its users in the Portland community.

> We have regularly scheduled monthly meetups (aggregate) and also host other events.

> Follow news about the group on Twitter at @pdxrlang

Next event is May 26 - Aggregate (more info on Meetup page)

---
# Be Respectful (Code of Conduct)

- We will be following the [PDX-R Code of Conduct](https://pdxrlang.com/code-of-conduct.html) tonight

> PDX R Meetup is dedicated to providing a harassment-free meetup experience for everyone regardless of gender, gender identity and expression, sexual orientation, disability, physical appearance, body size, race, age or religion. We do not tolerate harassment of meetup participants in any form. Sexual language and imagery is not appropriate for any meetup venue, including talks. PDX R meetup participants violating these rules may be sanctioned or expelled from meetup events at the discretion of the meetup organizers.

- Please refer any violations to Marley Buchman (michaelmbuchman@gmail.com, 503-577-4985)

---
# Who's speaking tonight

- Elliott Hohn, Analyst at the Freshwater Trust
- Marley Buchman, ECONorthwest
- Ted Laderas, DNAnexus
- Kelly O'Briant, RStudio